---
title: Lisa's Landing Page
output:
  html_document:
    includes:
      in_header: header.html
    theme:
      bootswatch: minty
---

Admin content examples are deployed when a branch is merged into main on github. All content to the Connect server in parallel using github actions. Any failures will be recorded in the deployment log, along with relevant error messages. 
 
Content deployed can be accessed through this admin dashboard. This works by prefacing each piece of content with `connect-admin-example` and then matching on the string to pull it into the connectwidgets document. Content publishing is forced, meaning that content doesn't need to be deleted or meaningfully updated to be deployed in order to test a successful deploy for a content type. 
 
Environment variables can be set during deployment, refer to: <https://github.com/rstudio/actions/tree/main/connect-publish#update-env> 
 
 For github actions further refer to: 
 
- Solutions article: <https://solutions.posit.co/operations/deploy-methods/ci-cd/github-actions/> 
- rstudo-actions sample yaml: <https://github.com/rstudio/actions/blob/main/examples/connect-publish.yaml> 

Older packages can be installed following the instructions [here](https://support.rstudio.com/hc/en-us/articles/219949047-Installing-older-versions-of-packages), or through renv.

Content: 

 - shiny-python 
 - shiny-r
 - dash-app
 - streamlit 
 - rmarkdown (connectwidgets)

```{r setup, include=FALSE}
# TODO: 
# Add tracking for static content (not just shiny)
library(connectwidgets)
library(dplyr)
library(lubridate)
library(connectapi) #remotes::install_github('rstudio/connectapi')
library(ggplot2)
library(tidyr)
library(purrr)
library(gt)
library(httr)
#library(connectViz)  #remotes::install_github("RinteRface/connectViz")
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

```

```{r}
client <- connectwidgets::connect(
  server  = Sys.getenv("CONNECT_SERVER"),
  api_key = Sys.getenv("CONNECT_API_KEY")
  )

all_content <- connectwidgets::content(client)

sample_content <- all_content %>%
  arrange(desc(updated_time)) 

```


## Admin Content

### Content

```{r card}
sample_content %>%
  filter(grepl("connect-admin-example",name)) %>%
  rsc_card()
```


### Real-Time Process Data

Get process data from the API <https://docs.posit.co/connect/api/#get-/v1/content/-guid-/jobs>

- Historical metrics capture data at the server level only
- The instrumentation data does not have memory info
- `connectapi::get_procs()` will return some information about memory and cpu usage https://pkgs.rstudio.com/connectapi/reference/get_procs.html


```{r}
client <- connectapi::connect(
  server  = Sys.getenv("CONNECT_SERVER"),
  api_key = Sys.getenv("CONNECT_API_KEY")
  )

# all running processes on the server (NOTE: this is only one server of an HA cluster, with no clear server identifier)
procs <- get_procs(client)

# myapp <- content_item(client, "myguid")
# 
# # running jobs for the node that you are on
# myapp$get_jobs()

print(procs)
```

### Links to admin dashboards for further metrics

- Workbench Admin Dashboard: <https://colorado.posit.co/rstudio/admin>
- Connect Admin Dashboard: <https://colorado.posit.co/rsc/connect/#/admin/metrics>
- Datadog: <https://rs-soleng.datadoghq.com/dashboard/lists> 
- Graph: [https://prom.colorado.posit.co/graph](https://prom.colorado.posit.co/graph "https://prom.colorado.posit.co/graph")
- Prometheus/Grafana: [https://grafana.colorado.posit.co/](https://grafana.colorado.posit.co/ "https://grafana.colorado.posit.co/")

